Trends of SDR in Thessaloniki

### 2023-06-26 Article.Rmd
Commit 2023-06-26 19:17

---
title:         "Trends of SDR in Thessaloniki"
# header-includes:
author:
  - name:         Natsis Athanasios
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
#    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  Campus Box 149
    city:         Thessaloniki
    # state:        State
    postcode:     54124
    country:      Greece
#  - code:         Another University
#    organization: Department
#    addressline:  A street 29
#    postcode:     2054 NX
#    city:         Manchester,
#    country:      The Netherlands
# footnote:
#   - code:         1
#     text:         "This is the first author footnote."
#   - code:         2
#     text:         "Another author footnote."
abstract: |
  Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions.
  It consists of two paragraphs.
keywords: 
  - GHI
  - SDR
  - Solar Brigthening/Dimming
journal:        "An awesome journal"
date:           "`r Sys.Date()`"
classoption:    preprint, 3p, authoryear
bibliography:   references.bib
linenumbers:          false
numbersections:       true
header-includes:
   # - \usepackage{subfig}
   - \usepackage{subcaption}

@@

@@

<!-- ### Radiation data quality check -->
<!-- The radiation quality is assured with a manual screening, aided by an automatic assessment process. -->
<!-- screening -->
A manual screening is performed, to remove inconsistencies and erroneous recordings, that can occur randomly or systematically, during the long continuous operation of the instrument.
<!-- Quality assurance -->
The manual screening is aided by a radiation data quality assurance procedure, adjusted for this site, based on methods of Long and Shi\ [-@long_automated_2008; -@Long2006].
Thus, problematic recordings have been excluded from further processing. 
Although it is not possible to detect all the bad data, the large number of data and the aggregation scheme we use, can provide us with accurate radiometric measurements, for the scope of this study.

@@

<!-- ### Data selection -->
Due to a significant measurement uncertainty near, the horizon, we have to exclude
all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we excluded data with Azimuth angle between 
$35^\circ$ and $120^\circ$ with SZA greater than $80^\circ$.
On the latter instances, Sun is systematically, not visible by the instrument's location.
<!-- 1au -->
To make the measurements comparable throughout the dataset, we adjusted all 1-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
Subsequently, we made all measurements relative to the Total Solar Irradiance (TSI) at $1 \text{au}$, in order to compensate for the Sun's intensity variability, using a homogenized time series of satellite TSI observations.
The TSI data we use, is a combination of data from NOAA [@Coddington2005] (for `r as.Date(TSIinfo[TSI_Source == "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source == "NOAA", End])`) and adjusted data from @TSIStsi (for `r as.Date(TSIinfo[TSI_Source != "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source != "NOAA", End])`).
As a result, we can present all radiation data as a fraction of Sun's TSI.

>>>>

---
title:         "Trends of SDR in Thessaloniki"
# header-includes:
author:
  - name:         Natsis Athanasios
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
#    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  Campus Box 149
    city:         Thessaloniki
    # state:        State
    postcode:     54124
    country:      Greece
#  - code:         Another University
#    organization: Department
#    addressline:  A street 29
#    postcode:     2054 NX
#    city:         Manchester,
#    country:      The Netherlands
# footnote:
#   - code:         1
#     text:         "This is the first author footnote."
#   - code:         2
#     text:         "Another author footnote."
abstract: |
  Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions.
  It consists of two paragraphs.
keywords: 
  - GHI
  - SDR
  - Solar Brigthening/Dimming
journal:         "An awesome journal"
date:            "`r Sys.Date()`"
classoption:     preprint, 3p, authoryear
bibliography:    references2.bib
linenumbers:     false
numbersections:  true
header-includes:
   # - \usepackage{subfig}
   - \usepackage{subcaption}

@@

```{r}
library(stringr)

lines   <- paste(readLines("./Article.Rmd"), collapse = "")
entries <- unique(str_match_all(lines, "@([a-zA-Z0-9]+)[,\\. \\?\\!\\]\\;]")[[1]][, 2])
entries <- grep("gmail|auth", entries, value = TRUE, invert = TRUE)

bib <- paste(readLines("./references2.bib"), collapse = "\n")
bib <- unlist(strsplit(bib, "\n@"))

output <- sapply(entries, grep, bib, value = T)
output <- paste("@", output, sep = "")

writeLines(unlist(output), "./references3.bib")

```

@@

<!-- ### Radiation data quality check -->
<!-- The radiation quality is assured with a manual screening, aided by an automatic assessment process. -->
<!-- screening -->
A manual screening is performed, to remove inconsistencies and erroneous recordings, that can occur randomly or systematically, during the long continuous operation of the instrument.
<!-- Quality assurance -->
The manual screening is aided by a radiation data quality assurance procedure, adjusted for this site, based on methods of Long and Shi\ [-@Long2008; -@Long2006].
Thus, problematic recordings have been excluded from further processing. 
Although it is not possible to detect all the bad data, the large number of data and the aggregation scheme we use, can provide us with accurate radiometric measurements, for the scope of this study.

@@

<!-- ### Data selection -->
Due to a significant measurement uncertainty near, the horizon, we have to exclude
all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we excluded data with Azimuth angle between 
$35^\circ$ and $120^\circ$ with SZA greater than $80^\circ$.
On the latter instances, Sun is systematically, not visible by the instrument's location.
<!-- 1au -->
To make the measurements comparable throughout the dataset, we adjusted all 1-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
Subsequently, we made all measurements relative to the Total Solar Irradiance (TSI) at $1 \text{au}$, in order to compensate for the Sun's intensity variability, using a homogenized time series of satellite TSI observations.
The TSI data we use, is a combination of data from NOAA [@Coddington2005] (for `r as.Date(TSIinfo[TSI_Source == "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source == "NOAA", End])`) and adjusted data from @LASP2023 (for `r as.Date(TSIinfo[TSI_Source != "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source != "NOAA", End])`).
As a result, we can present all radiation data as a fraction of Sun's TSI.
